---
title: "Flow Reporting"
author: "Author"
output: officedown::rdocx_document
params:
  project_id: 0000
---

```{r setup, include=FALSE}
# ══════════════════════
# Initialisation section
# ══════════════════════
knitr::opts_chunk$set(echo = TRUE)

# Load Libraries
# ──────────────
library(tidyverse)
library(readxl)
library(ini)
library(flextable)
library(officer)
library(officedown)
library(conflicted)

# Load Functions and Globals
# ──────────────────────────

# Flextable borders
std_border <- fp_border(color = "gray")


# Glenday Palette
palGlenday <- scales::col_factor(
  palette = c('Green' = 'darkgreen', 'Yellow' = 'gold', 'Blue' = 'royalblue', 'Red' = 'red3'),
  levels = c('Green', 'Yellow', 'Blue', 'Red'))

# Load the data file
load('data_objects.RObj')
```

## Headlines

```{r RPT_01_headlines, echo = FALSE}
tbl <- flextable(df_headline_section) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(page_size = page_size(orient = 'portrait')))
```

## Changes in Activity

```{r RPT_02_changes_in_activity, echo = FALSE}
tbl <- flextable(df_activity_section) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(page_size = page_size(orient = 'portrait')))
```

## Changes in Activity (ED|EM|AMB)

```{r RPT_02a_changes_in_activity, echo = FALSE}
if(as.integer(params$project_id)!=2473)
  df_activity_section_em_ed_amb <- data.frame(metric = 'Not Applicable', current_month = NA, q1 = NA, q2 = NA, q3 = NA, q4 = NA, ytd = NA)

tbl <- flextable(df_activity_section_em_ed_amb) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(page_size = page_size(orient = 'portrait')))
```

## Process KPIs

```{r RPT_03_process_kpis, echo = FALSE}
tbl <- flextable(df_kpi_section) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(page_size = page_size(orient = 'portrait')))
```

## Data Points

```{r RPT_04_data_points, echo = FALSE}
tbl <- flextable(df_data_point_section) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(page_size = page_size(orient = 'portrait')))
```

## Support Provided

```{r RPT_05_support_provided, echo = FALSE}
tbl <- flextable(df_support_provided_section) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(type = 'continuous'))
```

## Outputs: Sections - Previous 3 months

```{r RPT_06_outputs_sections_prev_3m, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
txt_period_start_prev_3m <- if(dt_current_month - months(2) < dt_year_start){
  format(dt_year_start, '%b-%y')
} else {
  format(dt_current_month - months(2), '%b-%y')
}
txt_period_end_prev_3m <- format(dt_current_month, '%b-%y')

plt <- ggplot(data = df_outcomes_3m_section) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) %+%
  labs(title = paste0('Glenday Sieve Plot for Output Sections for the Previous 3 Months\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Output Section', y = 'Number of Outputs') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(section, 20), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outputs: Sections - Year to Date

```{r RPT_07_outputs_sections_ytd, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
txt_period_start_ytd <- format(dt_year_start, '%b-%y')
txt_period_end_ytd <- format(dt_current_month, '%b-%y')

plt <- ggplot(data = df_outputs_12m_section) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) %+%
  labs(title = paste0('Glenday Sieve Plot for Output Sections for the Year to Date\n',
                      txt_period_start_ytd, ' to ', txt_period_end_ytd),
       x = 'Output Section', y = 'Number of Outputs') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(section, 20), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outputs: Sections and Outputs - Previous 3 months

```{r RPT_08_outputs_sections_and_outputs_prev_3m, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_outputs_3m_section_metric %>% dplyr::filter(glenday=='Green')) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) %+%
  labs(title = paste0('Glenday Sieve Plot (Green only) for Outputs for the Previous 3 Months\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Output', y = 'Number of Outputs') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(output, 30), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outputs: Sections and Outputs - Year to Date

```{r RPT_09_outputs_sections_and_outputs_ytd, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_outputs_12m_section_metric %>% dplyr::filter(glenday=='Green')) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) %+%
  labs(title = paste0('Glenday Sieve Plot (Green only) for Outputs for the Year to Date\n',
                      txt_period_start_ytd, ' to ', txt_period_end_ytd),
       x = 'Output', y = 'Number of Outputs') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(output, 30), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outcomes: Sections - Previous 3 months

```{r RPT_10_outcomes_sections_prev_3m, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_outcomes_3m_section) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) %+%
  labs(title = paste0('Glenday Sieve Plot for Outcome Sections for the Previous 3 Months\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Outcome Section', y = 'Number of Outcomes') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(section, 20), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outcomes: Sections - Year to Date

```{r RPT_11_outcomes_sections_ytd, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_outcomes_12m_section) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) %+%
  labs(title = paste0('Glenday Sieve Plot for Outcome Sections for the Year to Date\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Outcome Section', y = 'Number of Outcomes') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(section, 20), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outcomes: Sections and Outcomes - Previous 3 months

```{r RPT_12_outcomes_sections_and_outcomes_prev_3m, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_outcomes_3m_section_metric %>% dplyr::filter(glenday=='Green')) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) %+%
  labs(title = paste0('Glenday Sieve Plot (Green only) for Outcomes for the Previous 3 Months\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Outcome', y = 'Number of Outcomes') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(outcome, 30), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outcomes: Sections and Outcomes - Year to Date

```{r RPT_13_outcomes_sections_and_outcomes_ytd, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_outcomes_12m_section_metric %>% dplyr::filter(glenday=='Green')) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) %+%
  labs(title = paste0('Glenday Sieve Plot (Green only) for Outcomes for the Year to Date\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Outcome', y = 'Number of Outcomes') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(outcome, 30), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

