---
title: "High Flow"
author: "Richard Blackwell"
output: officedown::rdocx_document
params:
  year_start: 2024-01-01
  current_month: 2024-08-01
---

```{r setup, include=FALSE}
# ══════════════════════
# Initialisation section
# ══════════════════════
knitr::opts_chunk$set(echo = TRUE)

# Load Libraries
# ──────────────
library(tidyverse)
library(readxl)
library(ini)
library(flextable)
library(officer)
library(officedown)
library(conflicted)

# Load Functions and Globals
# ──────────────────────────

# Flextable borders
std_border <- fp_border(color = "gray")


# Glenday Palette
palGlenday <- scales::col_factor(
  palette = c('Green' = 'darkgreen', 'Yellow' = 'gold', 'Blue' = 'royalblue', 'Red' = 'red3'),
  levels = c('Green', 'Yellow', 'Blue', 'Red'))

# Glenday Sieve
fnGlenday <- function(df, var.x, var.y){
  df <- df %>%
    dplyr::filter(get(var.y) > 0) %>%
    arrange(desc(get(var.y)), get(var.x)) %>%
    mutate(pct = get(var.y)/ sum(get(var.y)),
           cumpct = cumsum(pct),
           lag_cumpct = dplyr::lag(cumpct),
           glenday = if_else(cumpct <= 0.5 | (lag_cumpct < 0.5 & cumpct > 0.5),
                             'Green',
                             if_else(cumpct <= 0.95 | (lag_cumpct < 0.95 & cumpct > 0.95),
                                     'Yellow',
                                     if_else(cumpct <= 0.99 | (lag_cumpct < 0.99 & cumpct > 0.99),
                                             'Blue','Red')))) %>%
    select(-lag_cumpct) %>%
    # Replace any NA values in glenday as Green
    replace_na(replace = list(glenday = 'Green'))
  return(df)
}

# New clients supported - Ignore those that are in the exclusion list i.e "Declined", "No engagement"
fnNewClientsSupported <- function(df, period_start, period_end){
  df_report <- df_caseload_tracker %>% 
    dplyr::filter(ct_start >= period_start & ct_start < period_end) %>%
    dplyr::filter(!(ct_closure %in% unlist(unname(ini_file_settings$caseload_tracker_exclusions))))
  return(df_report)  
}

# All clients supported - Ignore those that are in the exclusion list i.e "Declined", "No engagement"
fnClientsSupported <- function(df, period_start, period_end){
  df_report <- df_caseload_tracker %>% 
    dplyr::filter(ct_start < period_end & (ct_end >= period_start | is.na(ct_end))) %>%
    dplyr::filter(!(ct_closure %in% unlist(unname(ini_file_settings$caseload_tracker_exclusions))))
  return(df_report)  
}

# Total new clients - simple count of new clients (ignoring exclusions)
fnTotalNewClients <- function(df, period_start, period_end){
  df_report <- df_caseload_tracker %>% 
    dplyr::filter(ct_start >= period_start & ct_start < period_end)
  return(df_report)
}

# Caseload - simple count of clients open at the end of the period
fnCaseload <- function(df, period_start, period_end){
  df_report <- df_caseload_tracker %>% 
    dplyr::filter(ct_start <= period_end & ( is.na(ct_end) | (ct_end >= period_end)))
  return(df_report)
}

# Clients at end of support - Ignore those that are in the exclusion list i.e "Declined", "No engagement"
fnClientsSupportedEnd <- function(df, period_start, period_end){
  df_report <- df_caseload_tracker %>% 
    dplyr::filter(ct_end >= period_start & ct_end < period_end) %>%
    dplyr::filter(!(ct_closure %in% unlist(unname(ini_file_settings$caseload_tracker_exclusions))))
  return(df_report)
}

# # Clients open during period - Not counting those that closed during the period
# fnTotalOpenClients <- function(df, period_start, period_end){
#   df_report <- df_caseload_tracker %>% 
#     dplyr::filter(ct_start < period_end & (ct_end > period_end | is.na(ct_end)))
#   return(df_report)
# }

# Read in the initialisation file settings
ini_file_settings <- read.ini('flow_reporting.ini')


# Time periods
dt_year_start <- as.Date(params$year_start)
dt_current_month <- as.Date(params$current_month)
# dt_year_start <- as.Date('2024-01-01')
# dt_current_month <- as.Date('2024-04-01')

# ═══════════════════════════════
# import_reporting_workbooks ----
# ═══════════════════════════════

# ════════════════════
# Import the workbooks
# ════════════════════

# Initialise data frames to receive the different sections of the workbooks
df_data_points <- data.frame()
df_support_and_referrals <- data.frame()
df_outputs <- data.frame()
df_outcomes <- data.frame()

# Loop through each of the reporting workbooks
for(f in ini_file_settings$reporting_workbooks){
  # ────────────────────────────────
  # Import the data points worksheet
  # ────────────────────────────────
  
  # Only import the first 3 columns of the sheet and set the variable type
  df_tmp <- read_excel(path = f, 
                       sheet = 'Data Points', 
                       range = cell_cols('A:C'), 
                       col_types = c('date','text','numeric')) %>%
    # Rename the column names as previously these have overwritten by caseworkers
    rename_with(.fn = ~c('month', 'metric', 'value')) %>% 
    # Remove any rows that have no month or no value
    dplyr::filter(!is.na(month) & !is.na(value)) %>%
    # Add the source filename to the data
    mutate(source = basename(file.path(f)))
  
  # Bind to the combined data frame
  df_data_points <- df_data_points %>% bind_rows(df_tmp)
  
  # ──────────────────────────────────────────
  # Import the support and referrals worksheet
  # ──────────────────────────────────────────
  
  # Only import the first 4 columns of the sheet and set the variable type
  df_tmp <- read_excel(path = f, 
                       sheet = 'Support and Referrals', 
                       range = cell_cols('A:D'), 
                       col_types = c('text','date','text','text')) %>%
    # Rename the column names as previously these have overwritten by caseworkers
    rename_with(.fn = ~c('client_id', 'month', 'section', 'support')) %>% 
    # Remove any rows that have an NA in column
    dplyr::filter( !(is.na(client_id) | is.na(month) | is.na(section) | is.na(support))) %>%
    # Add the source filename to the data
    mutate(source = basename(file.path(f)))
  
  # Bind to the combined data frame
  df_support_and_referrals <- df_support_and_referrals %>% bind_rows(df_tmp)
  
  # ────────────────────────────
  # Import the outputs worksheet
  # ────────────────────────────
  
  # Only import the first 4 columns of the sheet and set the variable type
  df_tmp <- read_excel(path = f, 
                       sheet = 'Outputs', 
                       range = cell_cols('A:D'), 
                       col_types = c('text','date','text','text')) %>%
    # Rename the column names as previously these have overwritten by caseworkers
    rename_with(.fn = ~c('client_id', 'month', 'section', 'output')) %>% 
    # Remove any rows that have an NA in column
    dplyr::filter( !(is.na(client_id) | is.na(month) | is.na(section) | is.na(output))) %>%
    # Add the source filename to the data
    mutate(source = basename(file.path(f)))
  
  # Bind to the combined data frame
  df_outputs <- df_outputs %>% bind_rows(df_tmp)
  
  # ─────────────────────────────
  # Import the outcomes worksheet
  # ─────────────────────────────
  
  # Only import the first 4 columns of the sheet and set the variable type
  df_tmp <- read_excel(path = f, 
                       sheet = 'Outcomes', 
                       range = cell_cols('A:D'), 
                       col_types = c('text','date','text','text')) %>%
    # Rename the column names as previously these have overwritten by caseworkers
    rename_with(.fn = ~c('client_id', 'month', 'section', 'outcome')) %>% 
    # Remove any rows that have an NA in column
    dplyr::filter( !(is.na(client_id) | is.na(month) | is.na(section) | is.na(outcome))) %>%
    # Add the source filename to the data
    mutate(source = basename(file.path(f)))
  
  # Bind to the combined data frame
  df_outcomes <- df_outcomes %>% bind_rows(df_tmp)
}

# ═══════════════════════════════════════
# import_caseload_tracker_worksheets ----
# ═══════════════════════════════════════
# Initialise the data frame to receive the caseload tracker data
df_caseload_tracker <- data.frame()

# Get the worksheet names from the ini file settings
caseload_tracker_worksheets <- unname(unlist(ini_file_settings$caseload_tracker_sheets))

# Get the required field numbers from the ini file
caseload_tracker_field_numbers <- c(
  unlist(as.integer(unname(ini_file_settings$caseload_tracker_demographics))),
  unlist(as.integer(unname(ini_file_settings$caseload_tracker_numbers_supported))),
  unlist(as.integer(unname(ini_file_settings$caseload_tracker_activity))),
  unlist(as.integer(unname(ini_file_settings$caseload_tracker_wemwbs_goals))))

# Get the required field names from the ini file
caseload_tracker_field_names <- c(
  unlist(names(ini_file_settings$caseload_tracker_demographics)),
  unlist(names(ini_file_settings$caseload_tracker_numbers_supported)),
  unlist(names(ini_file_settings$caseload_tracker_activity)),
  unlist(names(ini_file_settings$caseload_tracker_wemwbs_goals)))


# Loop through each of the caseload tracker worksheets
for(s in caseload_tracker_worksheets){
  # Read in all bar the first two lines of the sheets (the headers)
  df_tmp <- read_excel(path = ini_file_settings$caseload_tracker$caseload_tracker, 
                       sheet = s,
                       col_type = 'text', 
                       col_names = FALSE,
                       skip = 3,
                       ) %>% 
    # Select the required fields and rename them
    select(all_of(caseload_tracker_field_numbers)) %>%
    rename_with(.fn = ~caseload_tracker_field_names) %>%
    # Ignore any rows that don't have an ID
    dplyr::filter(!is.na(ct_id))
  
  # Bind to the combined data frame
  df_caseload_tracker <- df_caseload_tracker %>% bind_rows(df_tmp)
}

# Format the columns to required format
df_caseload_tracker <- df_caseload_tracker %>% 
  mutate(ct_age = as.integer(ct_age),
         ct_status = as.factor(ct_status),
         ct_closure = as.factor(ct_closure),
         ct_start = as.Date(as.integer(ct_start), origin = '1899-12-30'),
         ct_end = as.Date(as.integer(ct_end), origin = '1899-12-30')) %>%
  mutate(across(.cols = all_of(c(unlist(names(ini_file_settings$caseload_tracker_activity)),
                          unlist(names(ini_file_settings$caseload_tracker_wemwbs_goals)))),
                .fns = as.integer))

# ══════════════════
# 1.1 Headlines ----
# ══════════════════

df_RPT_01_headlines <- data.frame(metric = as.character(),
                                  current_month = as.integer(),
                                  q1 = as.integer(),
                                  q2 = as.integer(),
                                  q3 = as.integer(),
                                  q4 = as.integer(),
                                  ytd = as.integer())

# Number of new people supported in the period
number_current_month <- fnNewClientsSupported(df = df_caseload_tracker, 
                                              period_start = dt_current_month, 
                                              period_end = dt_current_month + months(1)) %>% NROW()
number_Q1 <- ifelse(dt_current_month >= dt_year_start,
                    fnNewClientsSupported(df = df_caseload_tracker, 
                                          period_start = dt_year_start, 
                                          period_end = dt_year_start + months(3)) %>% NROW(),
                    NA)
number_Q2 <- ifelse(dt_current_month >= dt_year_start + months(3),
                    fnNewClientsSupported(df = df_caseload_tracker, 
                                          period_start = dt_year_start + months(3), 
                                          period_end = dt_year_start + months(6)) %>% NROW(),
                    NA)
number_Q3 <- ifelse(dt_current_month >= dt_year_start + months(6),
                    fnNewClientsSupported(df = df_caseload_tracker, 
                                          period_start = dt_year_start + months(6), 
                                          period_end = dt_year_start + months(9)) %>% NROW(),
                    NA)
number_Q4 <- ifelse(dt_current_month >= dt_year_start + months(9),
                    fnNewClientsSupported(df = df_caseload_tracker, 
                                          period_start = dt_year_start + months(9), 
                                          period_end = dt_year_start + months(12)) %>% NROW(),
                    NA)
number_YTD <- fnNewClientsSupported(df = df_caseload_tracker, 
                                 period_start = dt_year_start, 
                                 period_end = dt_year_start + months(12)) %>% NROW()


df_RPT_01_headlines <- df_RPT_01_headlines %>% 
  bind_rows(data.frame(metric = 'New Clients Supported in Period',
                       current_month = number_current_month,
                       q1 = number_Q1,
                       q2 = number_Q2,
                       q3 = number_Q3,
                       q4 = number_Q4,
                       ytd = number_YTD))

# Number of people supported in the period
number_current_month <- fnClientsSupported(df = df_caseload_tracker, 
                                           period_start = dt_current_month, 
                                           period_end = dt_current_month + months(1)) %>% NROW()
number_Q1 <- ifelse(dt_current_month >= dt_year_start,
                    fnClientsSupported(df = df_caseload_tracker, 
                                       period_start = dt_year_start, 
                                       period_end = dt_year_start + months(3)) %>% NROW(),
                    NA)
number_Q2 <- ifelse(dt_current_month >= dt_year_start + months(3),
                    fnClientsSupported(df = df_caseload_tracker, 
                                       period_start = dt_year_start + months(3), 
                                       period_end = dt_year_start + months(6)) %>% NROW(),
                    NA)
number_Q3 <- ifelse(dt_current_month >= dt_year_start + months(6),
                    fnClientsSupported(df = df_caseload_tracker, 
                                       period_start = dt_year_start + months(6), 
                                       period_end = dt_year_start + months(9)) %>% NROW(),
                    NA)
number_Q4 <- ifelse(dt_current_month >= dt_year_start + months(9),
                    fnClientsSupported(df = df_caseload_tracker, 
                                       period_start = dt_year_start + months(9), 
                                       period_end = dt_year_start + months(12)) %>% NROW(),
                    NA)
number_YTD <- fnClientsSupported(df = df_caseload_tracker, 
                                 period_start = dt_year_start, 
                                 period_end = dt_year_start + months(12)) %>% NROW()

df_RPT_01_headlines <- df_RPT_01_headlines %>% 
  bind_rows(data.frame(metric = 'Clients Supported in Period',
                       current_month = number_current_month,
                       q1 = number_Q1,
                       q2 = number_Q2,
                       q3 = number_Q3,
                       q4 = number_Q4,
                       ytd = number_YTD))


# Emergency department, Emergency Admission and Ambulance conveyances count of people supported in the period
df_tmp <- fnClientsSupported(df = df_caseload_tracker, 
                             period_start = dt_current_month, 
                             period_end = dt_current_month + months(1))
number_current_month_ED_12m <- sum(df_tmp$ct_ed_12m, na.rm = TRUE)
number_current_month_EM_12m <- sum(df_tmp$ct_em_12m, na.rm = TRUE)
number_current_month_AMB_12m <- sum(df_tmp$ct_amb_12m, na.rm = TRUE)
number_current_month_ED_3m <- sum(df_tmp$ct_ed_3m, na.rm = TRUE)
number_current_month_EM_3m <- sum(df_tmp$ct_em_3m, na.rm = TRUE)
number_current_month_AMB_3m <- sum(df_tmp$ct_amb_3m, na.rm = TRUE)

if(dt_current_month >= dt_year_start){
  df_tmp <- fnClientsSupported(df = df_caseload_tracker, 
                               period_start = dt_year_start, 
                               period_end = dt_year_start + months(3))
  number_Q1_ED_12m <- sum(df_tmp$ct_ed_12m, na.rm = TRUE)
  number_Q1_EM_12m <- sum(df_tmp$ct_em_12m, na.rm = TRUE)
  number_Q1_AMB_12m <- sum(df_tmp$ct_amb_12m, na.rm = TRUE)
  number_Q1_ED_3m <- sum(df_tmp$ct_ed_3m, na.rm = TRUE)
  number_Q1_EM_3m <- sum(df_tmp$ct_em_3m, na.rm = TRUE)
  number_Q1_AMB_3m <- sum(df_tmp$ct_amb_3m, na.rm = TRUE)
} else {
  number_Q1_ED_12m <- NA
  number_Q1_EM_12m <- NA
  number_Q1_AMB_12m <- NA
  number_Q1_ED_3m <- NA
  number_Q1_EM_3m <- NA
  number_Q1_AMB_3m <- NA
}

if(dt_current_month >= dt_year_start + months(3)){
  df_tmp <- fnClientsSupported(df = df_caseload_tracker, 
                               period_start = dt_year_start + months(3), 
                               period_end = dt_year_start + months(6))
  number_Q2_ED_12m <- sum(df_tmp$ct_ed_12m, na.rm = TRUE)
  number_Q2_EM_12m <- sum(df_tmp$ct_em_12m, na.rm = TRUE)
  number_Q2_AMB_12m <- sum(df_tmp$ct_amb_12m, na.rm = TRUE)
  number_Q2_ED_3m <- sum(df_tmp$ct_ed_3m, na.rm = TRUE)
  number_Q2_EM_3m <- sum(df_tmp$ct_em_3m, na.rm = TRUE)
  number_Q2_AMB_3m <- sum(df_tmp$ct_amb_3m, na.rm = TRUE)
} else {
  number_Q2_ED_12m <- NA
  number_Q2_EM_12m <- NA
  number_Q2_AMB_12m <- NA
  number_Q2_ED_3m <- NA
  number_Q2_EM_3m <- NA
  number_Q2_AMB_3m <- NA
}

if(dt_current_month >= dt_year_start + months(6)){
  df_tmp <- fnClientsSupported(df = df_caseload_tracker, 
                               period_start = dt_year_start + months(6), 
                               period_end = dt_year_start + months(9))
  number_Q3_ED_12m <- sum(df_tmp$ct_ed_12m, na.rm = TRUE)
  number_Q3_EM_12m <- sum(df_tmp$ct_em_12m, na.rm = TRUE)
  number_Q3_AMB_12m <- sum(df_tmp$ct_amb_12m, na.rm = TRUE)
  number_Q3_ED_3m <- sum(df_tmp$ct_ed_3m, na.rm = TRUE)
  number_Q3_EM_3m <- sum(df_tmp$ct_em_3m, na.rm = TRUE)
  number_Q3_AMB_3m <- sum(df_tmp$ct_amb_3m, na.rm = TRUE)
} else {
  number_Q3_ED_12m <- NA
  number_Q3_EM_12m <- NA
  number_Q3_AMB_12m <- NA
  number_Q3_ED_3m <- NA
  number_Q3_EM_3m <- NA
  number_Q3_AMB_3m <- NA
}

if(dt_current_month >= dt_year_start + months(9)){
  df_tmp <- fnClientsSupported(df = df_caseload_tracker, 
                               period_start = dt_year_start + months(9), 
                               period_end = dt_year_start + months(12))
  number_Q4_ED_12m <- sum(df_tmp$ct_ed_12m, na.rm = TRUE)
  number_Q4_EM_12m <- sum(df_tmp$ct_em_12m, na.rm = TRUE)
  number_Q4_AMB_12m <- sum(df_tmp$ct_amb_12m, na.rm = TRUE)
  number_Q4_ED_3m <- sum(df_tmp$ct_ed_3m, na.rm = TRUE)
  number_Q4_EM_3m <- sum(df_tmp$ct_em_3m, na.rm = TRUE)
  number_Q4_AMB_3m <- sum(df_tmp$ct_amb_3m, na.rm = TRUE)
} else {
  number_Q4_ED_12m <- NA
  number_Q4_EM_12m <- NA
  number_Q4_AMB_12m <- NA
  number_Q4_ED_3m <- NA
  number_Q4_EM_3m <- NA
  number_Q4_AMB_3m <- NA
}

number_YTD <- fnClientsSupported(df = df_caseload_tracker, 
                                 period_start = dt_year_start, 
                                 period_end = dt_year_start + months(12)) %>% NROW()

df_tmp <- fnClientsSupported(df = df_caseload_tracker, 
                             period_start = dt_year_start, 
                             period_end = dt_year_start + months(12))
number_YTD_ED_12m <- sum(df_tmp$ct_ed_12m, na.rm = TRUE)
number_YTD_EM_12m <- sum(df_tmp$ct_em_12m, na.rm = TRUE)
number_YTD_AMB_12m <- sum(df_tmp$ct_amb_12m, na.rm = TRUE)
number_YTD_ED_3m <- sum(df_tmp$ct_ed_3m, na.rm = TRUE)
number_YTD_EM_3m <- sum(df_tmp$ct_em_3m, na.rm = TRUE)
number_YTD_AMB_3m <- sum(df_tmp$ct_amb_3m, na.rm = TRUE)

df_RPT_01_headlines <- df_RPT_01_headlines %>% 
  bind_rows(data.frame(metric = 'Previous 12 Month ED Attendances for Clients Supported in Period',
                       current_month = number_current_month_ED_12m,
                       q1 = number_Q1_ED_12m,
                       q2 = number_Q2_ED_12m,
                       q3 = number_Q3_ED_12m,
                       q4 = number_Q4_ED_12m,
                       ytd = number_YTD_ED_12m)) %>%
  bind_rows(data.frame(metric = 'Previous 12 Month Emergency Admissions for Clients Supported in Period',
                       current_month = number_current_month_EM_12m,
                       q1 = number_Q1_EM_12m,
                       q2 = number_Q2_EM_12m,
                       q3 = number_Q3_EM_12m,
                       q4 = number_Q4_EM_12m,
                       ytd = number_YTD_EM_12m)) %>%
  bind_rows(data.frame(metric = 'Previous 12 Month Ambulance Conveyances for Clients Supported in Period',
                       current_month = number_current_month_AMB_12m,
                       q1 = number_Q1_AMB_12m,
                       q2 = number_Q2_AMB_12m,
                       q3 = number_Q3_AMB_12m,
                       q4 = number_Q4_AMB_12m,
                       ytd = number_YTD_AMB_12m)) %>%
  bind_rows(data.frame(metric = 'Previous 3 Month ED Attendances for Clients Supported in Period',
                       current_month = number_current_month_ED_3m,
                       q1 = number_Q1_ED_3m,
                       q2 = number_Q2_ED_3m,
                       q3 = number_Q3_ED_3m,
                       q4 = number_Q4_ED_3m,
                       ytd = number_YTD_ED_3m)) %>%
  bind_rows(data.frame(metric = 'Previous 3 Month Emergency Admissions for Clients Supported in Period',
                       current_month = number_current_month_EM_3m,
                       q1 = number_Q1_EM_3m,
                       q2 = number_Q2_EM_3m,
                       q3 = number_Q3_EM_3m,
                       q4 = number_Q4_EM_3m,
                       ytd = number_YTD_EM_3m)) %>%
  bind_rows(data.frame(metric = 'Previous 3 Month Ambulance Conveyances for Clients Supported in Period',
                       current_month = number_current_month_AMB_3m,
                       q1 = number_Q1_AMB_3m,
                       q2 = number_Q2_AMB_3m,
                       q3 = number_Q3_AMB_3m,
                       q4 = number_Q4_AMB_3m,
                       ytd = number_YTD_AMB_3m))
df_RPT_01_headlines

# ════════════════════════════════════════════════════════
# 2.1  Changes in activity / tracking - NHSE/OND KPIs ----
# ════════════════════════════════════════════════════════

# This first section will need to be re-written when the ED|EM|AMB data sheet is
# provided by RDUH BI team
df_RPT_02_changes_in_activity <- df_RPT_01_headlines %>% dplyr::filter(metric=='New Clients Supported in Period') %>%
  bind_rows(
    data.frame(metric = c('Reduction in ED attendances starting 3 months from intervention beginning (NHSE Target 40%)',
                          'Reduction in non elective admissions 3 months from intervention beginning (NHSE Target 40%)',
                          'Reduction in ambulance conveyances 3 months from intervention beginning (No NHSE Target)',
                          'Reduction in ED attendances 12 month prior to 12 months post (OND Target 40%)',
                          'Reduction in Non elective admissions 12 months prior to 12 months post. (OND Target 40%)',
                          'Reduction in ambulance conveyances 12 months from intervention beginning (No NHSE Target)',
                          'Reduction in people experiencing loneliness at the end of support (NHSE Target 66%)'),
               current_month = rep(NA, 7),
               q1 = rep(NA, 7),
               q2 = rep(NA, 7),
               q3 = rep(NA, 7),
               q4 = rep(NA, 7),
               ytd = rep(NA, 7)))

# Clients at end of support
df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                period_start = dt_current_month, 
                                period_end = dt_current_month + months(1))
number_current_month <- df_tmp %>% NROW()
number_current_month_increased_wemwbs <- sum((df_tmp$ct_wemwbs_score_out > df_tmp$ct_wemwbs_score_in ) * 1, na.rm = TRUE)
number_current_month_goals_progressed <- sum(
  (
    (df_tmp$ct_goals_mh_out > df_tmp$ct_goals_mh_in) | 
    (df_tmp$ct_goals_ph_out > df_tmp$ct_goals_ph_in) | 
    (df_tmp$ct_goals_housing_out > df_tmp$ct_goals_housing_in) | 
    (df_tmp$ct_goals_diet_out > df_tmp$ct_goals_diet_in) | 
    (df_tmp$ct_goals_relations_out > df_tmp$ct_goals_relations_in) | 
    (df_tmp$ct_goals_money_out > df_tmp$ct_goals_money_in) | 
    (df_tmp$ct_goals_growth_out > df_tmp$ct_goals_growth_in) | 
    (df_tmp$ct_goals_community_out > df_tmp$ct_goals_community_in) | 
    (df_tmp$ct_goals_abuse_out > df_tmp$ct_goals_abuse_in) | 
    (df_tmp$ct_goals_children_out > df_tmp$ct_goals_children_in)
  ) * 1,
  na.rm = TRUE)


if(dt_current_month >= dt_year_start){
  df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                  period_start = dt_year_start, 
                                  period_end = dt_year_start + months(3))
  number_Q1 <- df_tmp %>% NROW()
  number_Q1_increased_wemwbs <- sum((df_tmp$ct_wemwbs_score_out > df_tmp$ct_wemwbs_score_in ) * 1, na.rm = TRUE)
  number_Q1_goals_progressed <- sum((
    (df_tmp$ct_goals_mh_out > df_tmp$ct_goals_mh_in) | (df_tmp$ct_goals_ph_out > df_tmp$ct_goals_ph_in) | (df_tmp$ct_goals_housing_out > df_tmp$ct_goals_housing_in) | 
      (df_tmp$ct_goals_diet_out > df_tmp$ct_goals_diet_in) | (df_tmp$ct_goals_relations_out > df_tmp$ct_goals_relations_in) | (df_tmp$ct_goals_money_out > df_tmp$ct_goals_money_in) | 
      (df_tmp$ct_goals_growth_out > df_tmp$ct_goals_growth_in) | (df_tmp$ct_goals_community_out > df_tmp$ct_goals_community_in) | (df_tmp$ct_goals_abuse_out > df_tmp$ct_goals_abuse_in) | 
      (df_tmp$ct_goals_children_out > df_tmp$ct_goals_children_in)) * 1, na.rm = TRUE)
} else {
  number_Q1 <- NA
  number_Q1_increased_wemwbs <- NA
  number_Q1_goals_progressed <- NA
}

if(dt_current_month >= dt_year_start + months(3)){
  df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                  period_start = dt_year_start + months(3), 
                                  period_end = dt_year_start + months(6))
  number_Q2 <- df_tmp %>% NROW()
  number_Q2_increased_wemwbs <- sum((df_tmp$ct_wemwbs_score_out > df_tmp$ct_wemwbs_score_in ) * 1, na.rm = TRUE)
  number_Q2_goals_progressed <- sum((
    (df_tmp$ct_goals_mh_out > df_tmp$ct_goals_mh_in) | (df_tmp$ct_goals_ph_out > df_tmp$ct_goals_ph_in) | (df_tmp$ct_goals_housing_out > df_tmp$ct_goals_housing_in) | 
      (df_tmp$ct_goals_diet_out > df_tmp$ct_goals_diet_in) | (df_tmp$ct_goals_relations_out > df_tmp$ct_goals_relations_in) | (df_tmp$ct_goals_money_out > df_tmp$ct_goals_money_in) | 
      (df_tmp$ct_goals_growth_out > df_tmp$ct_goals_growth_in) | (df_tmp$ct_goals_community_out > df_tmp$ct_goals_community_in) | (df_tmp$ct_goals_abuse_out > df_tmp$ct_goals_abuse_in) | 
      (df_tmp$ct_goals_children_out > df_tmp$ct_goals_children_in)) * 1, na.rm = TRUE)
} else {
  number_Q2 <- NA
  number_Q2_increased_wemwbs <- NA
  number_Q2_goals_progressed <- NA
}

if(dt_current_month >= dt_year_start + months(6)){
  df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                  period_start = dt_year_start + months(6), 
                                  period_end = dt_year_start + months(9))
  number_Q3 <- df_tmp %>% NROW()
  number_Q3_increased_wemwbs <- sum((df_tmp$ct_wemwbs_score_out > df_tmp$ct_wemwbs_score_in ) * 1, na.rm = TRUE)
  number_Q3_goals_progressed <- sum((
    (df_tmp$ct_goals_mh_out > df_tmp$ct_goals_mh_in) | (df_tmp$ct_goals_ph_out > df_tmp$ct_goals_ph_in) | (df_tmp$ct_goals_housing_out > df_tmp$ct_goals_housing_in) | 
      (df_tmp$ct_goals_diet_out > df_tmp$ct_goals_diet_in) | (df_tmp$ct_goals_relations_out > df_tmp$ct_goals_relations_in) | (df_tmp$ct_goals_money_out > df_tmp$ct_goals_money_in) | 
      (df_tmp$ct_goals_growth_out > df_tmp$ct_goals_growth_in) | (df_tmp$ct_goals_community_out > df_tmp$ct_goals_community_in) | (df_tmp$ct_goals_abuse_out > df_tmp$ct_goals_abuse_in) | 
      (df_tmp$ct_goals_children_out > df_tmp$ct_goals_children_in)) * 1, na.rm = TRUE)
} else {
  number_Q3 <- NA
  number_Q3_increased_wemwbs <- NA
  number_Q3_goals_progressed <- NA
}

if(dt_current_month >= dt_year_start + months(9)){
  df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                  period_start = dt_year_start + months(9), 
                                  period_end = dt_year_start + months(12))
  number_Q4 <- df_tmp %>% NROW()
  number_Q4_increased_wemwbs <- sum((df_tmp$ct_wemwbs_score_out > df_tmp$ct_wemwbs_score_in ) * 1, na.rm = TRUE)
  number_Q4_goals_progressed <- sum((
    (df_tmp$ct_goals_mh_out > df_tmp$ct_goals_mh_in) | (df_tmp$ct_goals_ph_out > df_tmp$ct_goals_ph_in) | (df_tmp$ct_goals_housing_out > df_tmp$ct_goals_housing_in) | 
      (df_tmp$ct_goals_diet_out > df_tmp$ct_goals_diet_in) | (df_tmp$ct_goals_relations_out > df_tmp$ct_goals_relations_in) | (df_tmp$ct_goals_money_out > df_tmp$ct_goals_money_in) | 
      (df_tmp$ct_goals_growth_out > df_tmp$ct_goals_growth_in) | (df_tmp$ct_goals_community_out > df_tmp$ct_goals_community_in) | (df_tmp$ct_goals_abuse_out > df_tmp$ct_goals_abuse_in) | 
      (df_tmp$ct_goals_children_out > df_tmp$ct_goals_children_in)) * 1, na.rm = TRUE)
} else {
  number_Q4 <- NA
  number_Q4_increased_wemwbs <- NA
  number_Q4_goals_progressed <- NA
}

df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                period_start = dt_year_start, 
                                period_end = dt_year_start + months(12))
number_YTD <- df_tmp %>% NROW()
number_YTD_increased_wemwbs <- sum((df_tmp$ct_wemwbs_score_out > df_tmp$ct_wemwbs_score_in ) * 1, na.rm = TRUE)
number_YTD_goals_progressed <- sum((
  (df_tmp$ct_goals_mh_out > df_tmp$ct_goals_mh_in) | (df_tmp$ct_goals_ph_out > df_tmp$ct_goals_ph_in) | (df_tmp$ct_goals_housing_out > df_tmp$ct_goals_housing_in) | 
    (df_tmp$ct_goals_diet_out > df_tmp$ct_goals_diet_in) | (df_tmp$ct_goals_relations_out > df_tmp$ct_goals_relations_in) | (df_tmp$ct_goals_money_out > df_tmp$ct_goals_money_in) | 
    (df_tmp$ct_goals_growth_out > df_tmp$ct_goals_growth_in) | (df_tmp$ct_goals_community_out > df_tmp$ct_goals_community_in) | (df_tmp$ct_goals_abuse_out > df_tmp$ct_goals_abuse_in) | 
    (df_tmp$ct_goals_children_out > df_tmp$ct_goals_children_in)) * 1, na.rm = TRUE)

df_RPT_02_changes_in_activity <- df_RPT_02_changes_in_activity %>% 
  bind_rows(data.frame(
    metric = c('Clients Ending Support', 'Clients ending Support and Experiencing Improved Wellbeing',
               'People report a positive experience from our support (NHSE Target 80%)',
               'People progress at least one goal (OND Target 90%)'),
    current_month = c(number_current_month, number_current_month_increased_wemwbs, NA, number_current_month_goals_progressed),
    q1 = c(number_Q1, number_Q1_increased_wemwbs, NA, number_Q1_goals_progressed),
    q2 = c(number_Q2, number_Q2_increased_wemwbs, NA, number_Q2_goals_progressed),
    q3 = c(number_Q3, number_Q3_increased_wemwbs, NA, number_Q3_goals_progressed),
    q4 = c(number_Q4, number_Q4_increased_wemwbs, NA, number_Q4_goals_progressed),
    ytd = c(number_YTD, number_YTD_increased_wemwbs, NA, number_YTD_goals_progressed)))

df_RPT_02_changes_in_activity

# ═════════════════════
# 2.2 Process KPIS ----
# ═════════════════════

df_tmp <- fnNewClientsSupported(df = df_caseload_tracker, 
                                period_start = dt_current_month, 
                                period_end = dt_current_month + months(1))
denominator_current_month <- df_tmp %>% NROW()
number_current_month_baseline_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_in)) %>% NROW()
number_current_month_loneliness_question <- df_tmp %>% dplyr::filter(ct_loneliness %in% c('Yes','No')) %>% NROW()
pct_current_month_baseline_wemwbs <- number_current_month_baseline_wemwbs / denominator_current_month
pct_current_month_loneliness_question <- number_current_month_loneliness_question / denominator_current_month

if(dt_current_month >= dt_year_start){
  df_tmp <- fnNewClientsSupported(df = df_caseload_tracker, 
                                  period_start = dt_year_start, 
                                  period_end = dt_year_start + months(3))
  denominator_Q1 <- df_tmp %>% NROW()
  number_Q1_baseline_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_in)) %>% NROW()
  number_Q1_loneliness_question <- df_tmp %>% dplyr::filter(ct_loneliness %in% c('Yes','No')) %>% NROW()
  pct_Q1_baseline_wemwbs <- number_Q1_baseline_wemwbs / denominator_Q1
  pct_Q1_loneliness_question <- number_Q1_loneliness_question / denominator_Q1
} else {
  denominator_Q1 <- NA
  number_Q1_baseline_wemwbs <- NA
  number_Q1_loneliness_question <- NA
  pct_Q1_baseline_wemwbs <- NA
  pct_Q1_loneliness_question <- NA
}

if(dt_current_month >= dt_year_start){
  df_tmp <- fnNewClientsSupported(df = df_caseload_tracker, 
                                  period_start = dt_year_start + months(3), 
                                  period_end = dt_year_start + months(6))
  denominator_Q2 <- df_tmp %>% NROW()
  number_Q2_baseline_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_in)) %>% NROW()
  number_Q2_loneliness_question <- df_tmp %>% dplyr::filter(ct_loneliness %in% c('Yes','No')) %>% NROW()
  pct_Q2_baseline_wemwbs <- number_Q2_baseline_wemwbs / denominator_Q2
  pct_Q2_loneliness_question <- number_Q2_loneliness_question / denominator_Q2
} else {
  denominator_Q2 <- NA
  number_Q2_baseline_wemwbs <- NA
  number_Q2_loneliness_question <- NA
  pct_Q2_baseline_wemwbs <- NA
  pct_Q2_loneliness_question <- NA
}
 
if(dt_current_month >= dt_year_start){
  df_tmp <- fnNewClientsSupported(df = df_caseload_tracker, 
                                  period_start = dt_year_start + months(6), 
                                  period_end = dt_year_start + months(9))
  denominator_Q3 <- df_tmp %>% NROW()
  number_Q3_baseline_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_in)) %>% NROW()
  number_Q3_loneliness_question <- df_tmp %>% dplyr::filter(ct_loneliness %in% c('Yes','No')) %>% NROW()
  pct_Q3_baseline_wemwbs <- number_Q3_baseline_wemwbs / denominator_Q3
  pct_Q3_loneliness_question <- number_Q3_loneliness_question / denominator_Q3
} else {
  denominator_Q3 <- NA
  number_Q3_baseline_wemwbs <- NA
  number_Q3_loneliness_question <- NA
  pct_Q3_baseline_wemwbs <- NA
  pct_Q3_loneliness_question <- NA
} 

if(dt_current_month >= dt_year_start){
  df_tmp <- fnNewClientsSupported(df = df_caseload_tracker, 
                                  period_start = dt_year_start + months(9), 
                                  period_end = dt_year_start + months(12))
  denominator_Q4 <- df_tmp %>% NROW()
  number_Q4_baseline_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_in)) %>% NROW()
  number_Q4_loneliness_question <- df_tmp %>% dplyr::filter(ct_loneliness %in% c('Yes','No')) %>% NROW()
  pct_Q4_baseline_wemwbs <- number_Q4_baseline_wemwbs / denominator_Q4
  pct_Q4_loneliness_question <- number_Q4_loneliness_question / denominator_Q4
} else {
  denominator_Q4 <- NA
  number_Q4_baseline_wemwbs <- NA
  number_Q4_loneliness_question <- NA
  pct_Q4_baseline_wemwbs <- NA
  pct_Q4_loneliness_question <- NA
} 

df_tmp <- fnNewClientsSupported(df = df_caseload_tracker, 
                                period_start = dt_year_start, 
                                period_end = dt_year_start + months(12))
denominator_YTD <- df_tmp %>% NROW()
number_YTD_baseline_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_in)) %>% NROW()
number_YTD_loneliness_question <- df_tmp %>% dplyr::filter(ct_loneliness %in% c('Yes','No')) %>% NROW()
pct_YTD_baseline_wemwbs <- number_YTD_baseline_wemwbs / denominator_YTD
pct_YTD_loneliness_question <- number_YTD_loneliness_question / denominator_YTD

# Exit questions

df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                period_start = dt_current_month, 
                                period_end = dt_current_month + months(1))
denominator_current_month_exit <- df_tmp %>% NROW()
number_current_month_exit_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_out)) %>% NROW()
number_current_month_exit_loneliness <- NA
pct_current_month_exit_wemwbs <- number_current_month_exit_wemwbs / denominator_current_month_exit
pct_current_month_exit_loneliness <- NA

if(dt_current_month >= dt_year_start){
  df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                  period_start = dt_year_start, 
                                  period_end = dt_year_start + months(3))
  denominator_Q1_exit <- df_tmp %>% NROW()
  number_Q1_exit_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_out)) %>% NROW()
  number_Q1_exit_loneliness <- NA
  pct_Q1_exit_wemwbs <- number_Q1_exit_wemwbs / denominator_Q1_exit
  pct_Q1_exit_loneliness <- NA
} else {
  denominator_Q1_exit <- NA
  number_Q1_exit_wemwbs <- NA
  number_Q1_exit_loneliness <- NA
  pct_Q1_exit_wemwbs <- NA
  pct_Q1_exit_loneliness <- NA
}

if(dt_current_month >= dt_year_start){
  df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                  period_start = dt_year_start + months(3), 
                                  period_end = dt_year_start + months(6))
  denominator_Q2_exit <- df_tmp %>% NROW()
  number_Q2_exit_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_out)) %>% NROW()
  number_Q2_exit_loneliness <- NA
  pct_Q2_exit_wemwbs <- number_Q2_exit_wemwbs / denominator_Q2_exit
  pct_Q2_exit_loneliness <- NA
} else {
  denominator_Q2_exit <- NA
  number_Q2_exit_wemwbs <- NA
  number_Q2_exit_loneliness <- NA
  pct_Q2_exit_wemwbs <- NA
  pct_Q2_exit_loneliness <- NA
}

if(dt_current_month >= dt_year_start){
  df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                  period_start = dt_year_start + months(6), 
                                  period_end = dt_year_start + months(9))
  denominator_Q3_exit <- df_tmp %>% NROW()
  number_Q3_exit_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_out)) %>% NROW()
  number_Q3_exit_loneliness <- NA
  pct_Q3_exit_wemwbs <- number_Q3_exit_wemwbs / denominator_Q3_exit
  pct_Q3_exit_loneliness <- NA
} else {
  denominator_Q3_exit <- NA
  number_Q3_exit_wemwbs <- NA
  number_Q3_exit_loneliness <- NA
  pct_Q3_exit_wemwbs <- NA
  pct_Q3_exit_loneliness <- NA
}

if(dt_current_month >= dt_year_start){
  df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                  period_start = dt_year_start + months(9), 
                                  period_end = dt_year_start + months(12))
  denominator_Q4_exit <- df_tmp %>% NROW()
  number_Q4_exit_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_out)) %>% NROW()
  number_Q4_exit_loneliness <- NA
  pct_Q4_exit_wemwbs <- number_Q4_exit_wemwbs / denominator_Q4_exit
  pct_Q4_exit_loneliness <- NA
} else {
  denominator_Q4_exit <- NA
  number_Q4_exit_wemwbs <- NA
  number_Q4_exit_loneliness <- NA
  pct_Q4_exit_wemwbs <- NA
  pct_Q4_exit_loneliness <- NA
}

df_tmp <- fnClientsSupportedEnd(df = df_caseload_tracker, 
                                period_start = dt_year_start, 
                                period_end = dt_year_start + months(12))
denominator_YTD_exit <- df_tmp %>% NROW()
number_YTD_exit_wemwbs <- df_tmp %>% dplyr::filter(!is.na(ct_wemwbs_score_out)) %>% NROW()
number_YTD_exit_loneliness <- NA
pct_YTD_exit_wemwbs <- number_YTD_exit_wemwbs / denominator_YTD_exit
pct_YTD_exit_loneliness <- NA

df_RPT_03_process_kpis <- data.frame(metric = c('80% of new clients has a wemwebs baseline score',
                                         '80% exited client has a wemwbs exit score',
                                         '80% of clients have a Y/N loneliness question',
                                         '80% client has a loneliness exit score'),
                              current_month = c(if_else(is.na(denominator_current_month), '', 
                                                        sprintf('%.1f%% (%d/%d)', 
                                                        pct_current_month_baseline_wemwbs*100, 
                                                        number_current_month_baseline_wemwbs,
                                                        denominator_current_month)),
                                                if_else(is.na(denominator_current_month_exit), '', 
                                                        sprintf('%.1f%% (%d/%d)', 
                                                        pct_current_month_exit_wemwbs*100,
                                                        number_current_month_exit_wemwbs,
                                                        denominator_current_month_exit)),
                                                if_else(is.na(denominator_current_month), '', 
                                                        sprintf('%.1f%% (%d/%d)', 
                                                        pct_current_month_loneliness_question*100,
                                                        number_current_month_loneliness_question,
                                                        denominator_current_month)),
                                                if_else(is.na(denominator_current_month_exit), '', 
                                                        sprintf('%.1f%% (%d/%d)', 
                                                        pct_current_month_exit_loneliness*100,
                                                        number_current_month_exit_loneliness,
                                                        denominator_current_month_exit))),
                              q1 = c(if_else(is.na(denominator_Q1), '', 
                                             sprintf('%.1f%% (%d/%d)',
                                             pct_Q1_baseline_wemwbs*100, 
                                             number_Q1_baseline_wemwbs,
                                             denominator_Q1)),
                                     if_else(is.na(denominator_Q1_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q1_exit_wemwbs*100,
                                             number_Q1_exit_wemwbs,
                                             denominator_Q1_exit)),
                                     if_else(is.na(denominator_Q1), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q1_loneliness_question*100,
                                             number_Q1_loneliness_question,
                                             denominator_Q1)),
                                     if_else(is.na(denominator_Q1_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q1_exit_loneliness*100,
                                             number_Q1_exit_loneliness,
                                             denominator_Q1_exit))),
                              q2 = c(if_else(is.na(denominator_Q2), '', 
                                             sprintf('%.1f%% (%d/%d)',
                                             pct_Q2_baseline_wemwbs*100, 
                                             number_Q2_baseline_wemwbs,
                                             denominator_Q2)),
                                     if_else(is.na(denominator_Q2_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q2_exit_wemwbs*100,
                                             number_Q2_exit_wemwbs,
                                             denominator_Q2_exit)),
                                     if_else(is.na(denominator_Q2), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q2_loneliness_question*100,
                                             number_Q2_loneliness_question,
                                             denominator_Q2)),
                                     if_else(is.na(denominator_Q2_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q2_exit_loneliness*100,
                                             number_Q2_exit_loneliness,
                                             denominator_Q2_exit))),
                              q3 = c(if_else(is.na(denominator_Q3), '', 
                                             sprintf('%.1f%% (%d/%d)',
                                             pct_Q3_baseline_wemwbs*100, 
                                             number_Q3_baseline_wemwbs,
                                             denominator_Q3)),
                                     if_else(is.na(denominator_Q3_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q3_exit_wemwbs*100,
                                             number_Q3_exit_wemwbs,
                                             denominator_Q3_exit)),
                                     if_else(is.na(denominator_Q3), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q3_loneliness_question*100,
                                             number_Q3_loneliness_question,
                                             denominator_Q3)),
                                     if_else(is.na(denominator_Q3_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q3_exit_loneliness*100,
                                             number_Q3_exit_loneliness,
                                             denominator_Q3_exit))),
                              q4 = c(if_else(is.na(denominator_Q4), '', 
                                             sprintf('%.1f%% (%d/%d)',
                                             pct_Q4_baseline_wemwbs*100, 
                                             number_Q4_baseline_wemwbs,
                                             denominator_Q4)),
                                     if_else(is.na(denominator_Q4_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q4_exit_wemwbs*100,
                                             number_Q4_exit_wemwbs,
                                             denominator_Q4_exit)),
                                     if_else(is.na(denominator_Q4), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q4_loneliness_question*100,
                                             number_Q4_loneliness_question,
                                             denominator_Q4)),
                                     if_else(is.na(denominator_Q4_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_Q4_exit_loneliness*100,
                                             number_Q4_exit_loneliness,
                                             denominator_Q4_exit))),
                              ytd = c(if_else(is.na(denominator_YTD), '', 
                                             sprintf('%.1f%% (%d/%d)',
                                             pct_YTD_baseline_wemwbs*100, 
                                             number_YTD_baseline_wemwbs,
                                             denominator_YTD)),
                                     if_else(is.na(denominator_YTD_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_YTD_exit_wemwbs*100,
                                             number_YTD_exit_wemwbs,
                                             denominator_YTD_exit)),
                                     if_else(is.na(denominator_YTD), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_YTD_loneliness_question*100,
                                             number_YTD_loneliness_question,
                                             denominator_YTD)),
                                     if_else(is.na(denominator_YTD_exit), '', 
                                             sprintf('%.1f%% (%d/%d)', 
                                             pct_YTD_exit_loneliness*100,
                                             number_YTD_exit_loneliness,
                                             denominator_YTD_exit))))
df_RPT_03_process_kpis

# ════════════════
# Data points ----
# ════════════════

# Process the Total current open cases (aka current caseload as at end of period)

caseload_current_month <- fnCaseload(df = df_caseload_tracker, 
                                     period_start = dt_current_month, 
                                     period_end = dt_current_month + months(1)) %>% NROW()

caseload_Q1 <- ifelse(dt_current_month >= dt_year_start,
                      fnCaseload(df = df_caseload_tracker, 
                                 period_start = dt_year_start, 
                                 period_end = dt_year_start + months(3)) %>% NROW(), NA)
caseload_Q2 <- ifelse(dt_current_month >= dt_year_start + months(3),
                      fnCaseload(df = df_caseload_tracker, 
                                 period_start = dt_year_start + months(3), 
                                 period_end = dt_year_start + months(6)) %>% NROW(), NA)
caseload_Q3 <- ifelse(dt_current_month >= dt_year_start + months(6),
                      fnCaseload(df = df_caseload_tracker, 
                                 period_start = dt_year_start + months(6), 
                                 period_end = dt_year_start + months(9)) %>% NROW(), NA)
caseload_Q4 <- ifelse(dt_current_month >= dt_year_start + months(9),
                      fnCaseload(df = df_caseload_tracker, 
                                 period_start = dt_year_start + months(9), 
                                 period_end = dt_year_start + months(12)) %>% NROW(), NA)
caseload_YTD <- fnCaseload(df = df_caseload_tracker, 
                           period_start = dt_year_start, 
                           period_end = dt_year_start + months(12)) %>% NROW()

df_tmp <- data.frame(
  metric = 'Current caseload', 
  current_month = caseload_current_month,
  q1 = caseload_Q1,
  q2 = caseload_Q2,
  q3 = caseload_Q3,
  q4 = caseload_Q4,
  ytd = caseload_YTD)

metrics <- c('Number of wider beneficiaries', 'Clients who declined', 
             'Case concluded successfully', 'Closed cases due to disengagement', 'Closed cases due to death',
             'Closed cases (other reasons, ie moving out of area)', 'Number of contacts/interventions with clients')
df_metrics <- data.frame(metric = factor(metrics, levels = metrics))

df_RPT_04_data_points <- df_metrics %>% 
  left_join(
    df_data_points %>%
      dplyr::filter(as.Date(month) == dt_current_month) %>%
      group_by(metric) %>%
      summarise(current_month = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'metric') %>%
  replace_na(replace = list('current_month' = 0)) %>%
  left_join(
    df_data_points %>%
      dplyr::filter(as.Date(month) >= dt_year_start & as.Date(month) < (dt_year_start + months(3))) %>%
      group_by(metric) %>%
      summarise(q1 = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'metric') %>%
  replace_na(replace = list('q1' = 0)) %>%
  left_join(
    df_data_points %>%
      dplyr::filter(as.Date(month) >= (dt_year_start + months(3)) & as.Date(month) < (dt_year_start + months(6))) %>%
      group_by(metric) %>%
      summarise(q2 = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'metric') %>%
  replace_na(replace = list('q2' = 0)) %>%
  left_join(
    df_data_points %>%
      dplyr::filter(as.Date(month) >= (dt_year_start + months(6)) & as.Date(month) < (dt_year_start + months(9))) %>%
      group_by(metric) %>%
      summarise(q3 = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'metric') %>%
  replace_na(replace = list('q3' = 0)) %>%
  left_join(
    df_data_points %>%
      dplyr::filter(as.Date(month) >= (dt_year_start + months(9)) & as.Date(month) < (dt_year_start + months(12))) %>%
      group_by(metric) %>%
      summarise(q4 = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'metric') %>%
  replace_na(replace = list('q4' = 0)) %>%
  left_join(
    df_data_points %>%
      dplyr::filter(as.Date(month) >= dt_year_start & as.Date(month) < (dt_year_start + months(12))) %>%
      group_by(metric) %>%
      summarise(ytd = sum(value, na.rm = TRUE)) %>%
      ungroup(),
    by = 'metric') %>%
  replace_na(replace = list('ytd' = 0)) %>%
  bind_rows(df_tmp)

df_RPT_04_data_points
  
# ═════════════════════
# support_provided ----
# ═════════════════════

metrics <- c('Team Around the Person meeting conducted', 'Flow meeting with FC & Lead Professional',
                'One-to-one work with clients (per client) number of individual one to one interactions with client',
                'Continued ongoing contacts with professionals (total number of seperate contacts)',
                'Caseworker research undertaken to find solutions for clients', 'Caseworker support to access Personal Health Budget',
                'Caseworker support with Form filling', 'Caseworker support with IT incl. virtual meetings, emails etc',
                'Caseworker support to meet aspirations', 'Client involved in coproduction work (total number of seperate contacts)')
df_metrics <- data.frame(metric = factor(metrics, levels = metrics))

df_RPT_05_support_provided <- df_metrics %>% 
  left_join(
    df_support_and_referrals %>%
      dplyr::filter(as.Date(month) == dt_current_month) %>%
      group_by(support) %>%
      summarise(current_month = n()) %>%
      ungroup(),
    by = c('metric' = 'support')) %>%
  replace_na(replace = list('current_month' = 0)) %>%
  left_join(
    df_support_and_referrals %>%
      dplyr::filter(as.Date(month) >= dt_year_start & as.Date(month) < (dt_year_start + months(3))) %>%
      group_by(support) %>%
      summarise(q1 = n()) %>%
      ungroup(),
    by = c('metric' = 'support')) %>%
  replace_na(replace = list('q1' = 0)) %>%
  left_join(
    df_support_and_referrals %>%
      dplyr::filter(as.Date(month) >= (dt_year_start + months(3)) & as.Date(month) < (dt_year_start + months(6))) %>%
      group_by(support) %>%
      summarise(q2 = n()) %>%
      ungroup(),
    by = c('metric' = 'support')) %>%
  replace_na(replace = list('q2' = 0)) %>%
  left_join(
    df_support_and_referrals %>%
      dplyr::filter(as.Date(month) >= (dt_year_start + months(6)) & as.Date(month) < (dt_year_start + months(9))) %>%
      group_by(support) %>%
      summarise(q3 = n()) %>%
      ungroup(),
    by = c('metric' = 'support')) %>%
  replace_na(replace = list('q3' = 0)) %>%
  left_join(
    df_support_and_referrals %>%
      dplyr::filter(as.Date(month) >= (dt_year_start + months(9)) & as.Date(month) < (dt_year_start + months(12))) %>%
      group_by(support) %>%
      summarise(q4 = n()) %>%
      ungroup(),
    by = c('metric' = 'support')) %>%
  replace_na(replace = list('q4' = 0)) %>%
  left_join(
    df_support_and_referrals %>%
      dplyr::filter(as.Date(month) >= dt_year_start & as.Date(month) < (dt_year_start + months(12))) %>%
      group_by(support) %>%
      summarise(ytd = n()) %>%
      ungroup(),
    by = c('metric' = 'support')) %>%
  replace_na(replace = list('ytd' = 0)) 

df_RPT_05_support_provided

# ═════════════════════
# Outputs_sections ----
# ═════════════════════

# For the visuals we will use YTD and past 3 months
df_outputs_sections_prev_3m <- df_outputs %>% 
  dplyr::filter(
    as.Date(month) >= (dt_current_month - months(2)) & 
      as.Date(month) < (dt_current_month + months(1)) &
      as.Date(month) >= dt_year_start) %>%
  group_by(section) %>%
  summarise(volume = n()) %>%
  ungroup()

df_RPT_06_outputs_sections_prev_3m <- fnGlenday(df_outputs_sections_prev_3m, var.x = 'section', var.y = 'volume')

df_outputs_sections_ytd <- df_outputs %>% 
  dplyr::filter(
    as.Date(month) >= dt_year_start & 
    as.Date(month) < (dt_current_month + months(1)) &
    as.Date(month) < (dt_year_start + months(12))
  ) %>%
  group_by(section) %>%
  summarise(volume = n()) %>%
  ungroup()

df_RPT_07_outputs_sections_ytd <- fnGlenday(df_outputs_sections_ytd, var.x = 'section', var.y = 'volume')

# ═════════════════════════════════
# Outputs_sections_and outputs ----
# ═════════════════════════════════

# For the visuals we will use YTD and past 3 months
df_outputs_sections_and_outputs_prev_3m <- df_outputs %>% 
  dplyr::filter(
    as.Date(month) >= (dt_current_month - months(2)) & 
      as.Date(month) < (dt_current_month + months(1)) &
      as.Date(month) >= dt_year_start) %>%
  group_by(section, output) %>%
  summarise(volume = n(),
            .groups = 'keep') %>%
  ungroup()

df_RPT_08_outputs_sections_and_outputs_prev_3m <- fnGlenday(df_outputs_sections_and_outputs_prev_3m, var.x = 'output', var.y = 'volume') 

df_outputs_sections_and_outputs_ytd <- df_outputs %>% 
  dplyr::filter(
    as.Date(month) >= dt_year_start & 
    as.Date(month) < (dt_current_month + months(1)) &
    as.Date(month) < (dt_year_start + months(12))
  ) %>%
  group_by(section, output) %>%
  summarise(volume = n(),
            .groups = 'keep') %>%
  ungroup()

df_RPT_09_outputs_sections_and_outputs_ytd <- fnGlenday(df_outputs_sections_and_outputs_ytd, var.x = 'output', var.y = 'volume') 

# ══════════════════════
# Outcomes_sections ----
# ══════════════════════

# For the visuals we will use YTD and past 3 months
df_outcomes_sections_prev_3m <- df_outcomes %>% 
  dplyr::filter(
    as.Date(month) >= (dt_current_month - months(2)) & 
      as.Date(month) < (dt_current_month + months(1)) &
      as.Date(month) >= dt_year_start) %>%
  group_by(section) %>%
  summarise(volume = n()) %>%
  ungroup()

df_RPT_10_outcomes_sections_prev_3m <- fnGlenday(df_outcomes_sections_prev_3m, var.x = 'section', var.y = 'volume')

df_outcomes_sections_ytd <- df_outcomes %>% 
  dplyr::filter(as.Date(month) >= dt_year_start) %>%
  group_by(section) %>%
  summarise(volume = n()) %>%
  ungroup()

df_RPT_11_outcomes_sections_ytd <- fnGlenday(df_outcomes_sections_ytd, var.x = 'section', var.y = 'volume')

# ═══════════════════════════════════
# Outcomes_sections_and_outcomes ----
# ═══════════════════════════════════

# For the visuals we will use YTD and past 3 months
df_outcomes_sections_and_outcomes_prev_3m <- df_outcomes %>% 
  dplyr::filter(
    as.Date(month) >= (dt_current_month - months(2)) & 
      as.Date(month) < (dt_current_month + months(1)) &
      as.Date(month) >= dt_year_start) %>%
  group_by(section, outcome) %>%
  summarise(volume = n(),
            .groups = 'keep') %>%
  ungroup()

df_RPT_12_outcomes_sections_and_outcomes_prev_3m <- fnGlenday(df_outcomes_sections_and_outcomes_prev_3m, var.x = 'outcome', var.y = 'volume') 

df_outcomes_sections_and_outcomes_ytd <- df_outcomes %>% 
  dplyr::filter(as.Date(month) >= dt_year_start) %>%
  group_by(section, outcome) %>%
  summarise(volume = n(),
            .groups = 'keep') %>%
  ungroup()

df_RPT_13_outcomes_sections_and_outcomes_ytd <- fnGlenday(df_outcomes_sections_and_outcomes_ytd, var.x = 'outcome', var.y = 'volume') 

save(list = c('df_caseload_tracker','df_data_points','df_support_and_referrals','df_outputs','df_outcomes'), file = paste0(format(Sys.time(), '%y%m%d_%H%M'), '.RObj'))
```

## Headlines

```{r RPT_01_headlines, echo = FALSE}
tbl <- flextable(df_RPT_01_headlines) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(page_size = page_size(orient = 'portrait')))
```

## Changes in Activity

```{r RPT_02_changes_in_activity, echo = FALSE}
tbl <- flextable(df_RPT_02_changes_in_activity) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(page_size = page_size(orient = 'portrait')))
```

## Process KPIs

```{r RPT_03_process_kpis, echo = FALSE}
tbl <- flextable(df_RPT_03_process_kpis) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(page_size = page_size(orient = 'portrait')))
```

## Data Points

```{r RPT_04_data_points, echo = FALSE}
tbl <- flextable(df_RPT_04_data_points) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(page_size = page_size(orient = 'portrait')))
```

## Support Provided

```{r RPT_05_support_provided, echo = FALSE}
tbl <- flextable(df_RPT_05_support_provided) %>%
  set_header_labels(
    metric = 'Metric',
    current_month = format(dt_current_month, '%b-%y'),
    q1 = 'Q1',
    q2 = 'Q2',
    q3 = 'Q3',
    q4 = 'Q4',
    ytd = 'YTD') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header")
tbl
block_section(prop_section(type = 'continuous'))
```

## Outputs: Sections - Previous 3 months

```{r RPT_06_outputs_sections_prev_3m, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
txt_period_start_prev_3m <- if(dt_current_month - months(2) < dt_year_start){
  format(dt_year_start, '%b-%y')
} else {
  format(dt_current_month - months(2), '%b-%y')
}
txt_period_end_prev_3m <- format(dt_current_month, '%b-%y')

plt <- ggplot(data = df_RPT_06_outputs_sections_prev_3m) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) %+%
  labs(title = paste0('Glenday Sieve Plot for Output Sections for the Previous 3 Months\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Output Section', y = 'Number of Outputs') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(section, 20), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outputs: Sections - Year to Date

```{r RPT_07_outputs_sections_ytd, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
txt_period_start_ytd <- format(dt_year_start, '%b-%y')
txt_period_end_ytd <- format(dt_current_month, '%b-%y')

plt <- ggplot(data = df_RPT_07_outputs_sections_ytd) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) %+%
  labs(title = paste0('Glenday Sieve Plot for Output Sections for the Year to Date\n',
                      txt_period_start_ytd, ' to ', txt_period_end_ytd),
       x = 'Output Section', y = 'Number of Outputs') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(section, 20), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outputs: Sections and Outputs - Previous 3 months

```{r RPT_08_outputs_sections_and_outputs_prev_3m, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_RPT_08_outputs_sections_and_outputs_prev_3m %>% dplyr::filter(glenday=='Green')) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) %+%
  labs(title = paste0('Glenday Sieve Plot (Green only) for Outputs for the Previous 3 Months\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Output', y = 'Number of Outputs') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(output, 30), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outputs: Sections and Outputs - Year to Date

```{r RPT_09_outputs_sections_and_outputs_ytd, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_RPT_09_outputs_sections_and_outputs_ytd %>% dplyr::filter(glenday=='Green')) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) %+%
  labs(title = paste0('Glenday Sieve Plot (Green only) for Outputs for the Year to Date\n',
                      txt_period_start_ytd, ' to ', txt_period_end_ytd),
       x = 'Output', y = 'Number of Outputs') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(output, 30), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outcomes: Sections - Previous 3 months

```{r RPT_10_outcomes_sections_prev_3m, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_RPT_10_outcomes_sections_prev_3m) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) %+%
  labs(title = paste0('Glenday Sieve Plot for Outcome Sections for the Previous 3 Months\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Outcome Section', y = 'Number of Outcomes') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(section, 20), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outcomes: Sections - Year to Date

```{r RPT_11_outcomes_sections_ytd, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_RPT_11_outcomes_sections_ytd) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) %+%
  labs(title = paste0('Glenday Sieve Plot for Outcome Sections for the Year to Date\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Outcome Section', y = 'Number of Outcomes') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(section, 20), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outcomes: Sections and Outcomes - Previous 3 months

```{r RPT_12_outcomes_sections_and_outcomes_prev_3m, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_RPT_12_outcomes_sections_and_outcomes_prev_3m %>% dplyr::filter(glenday=='Green')) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) %+%
  labs(title = paste0('Glenday Sieve Plot (Green only) for Outcomes for the Previous 3 Months\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Outcome', y = 'Number of Outcomes') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(outcome, 30), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

## Outcomes: Sections and Outcomes - Year to Date

```{r RPT_13_outcomes_sections_and_outcomes_ytd, echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "100%"}
plt <- ggplot(data = df_RPT_13_outcomes_sections_and_outcomes_ytd %>% dplyr::filter(glenday=='Green')) %+%
  theme_bw(base_size = 10) %+%
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) %+%
  labs(title = paste0('Glenday Sieve Plot (Green only) for Outcomes for the Year to Date\n',
                      txt_period_start_prev_3m, ' to ', txt_period_end_prev_3m),
       x = 'Outcome', y = 'Number of Outcomes') %+%
  guides(fill = guide_legend(title = 'Glenday Sieve')) %+%
  geom_bar(aes(x = forcats::fct_reorder(str_wrap(outcome, 30), -volume), y = volume, fill = glenday), stat = 'identity') %+%
  scale_fill_manual(values = c('Green' = 'darkgreen',
                               'Yellow' = 'gold',
                               'Blue' = 'royalblue',
                                'Red' = 'red3'),
                     breaks = c('Green','Yellow','Blue','Red'))
plt
block_section(prop_section(page_size = page_size(orient = 'landscape')))
```

